---
title: "Games&Reviews - a mini text-mining project"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    social: menu
    source: embed
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE,
                      warning = FALSE,
                      comment = NA,
                      eval=FALSE)
```

```{r include=FALSE}
library(tidyverse)
library(tidytext)
library(flexdashboard)
library(topicmodels)
library(lubridate)
library(stringr)
library(reshape2)
library(wordcloud)
library(wordcloud2)
library(DT)
library(forcats)
```

```{r include = FALSE}
nameList <- c('dota','Cities_skylines','Civilization','GTA5','pubg','Rocket_League')

dat <- data_frame()

for(name in nameList){
  temp <- read_csv(paste0(name,'.csv'))
  temp$gameId <- name
  dat <- bind_rows(dat,
                   temp)
  rm(temp)
}

clean <- function(x){
  x <- x %>% 
    str_to_lower() %>% 
    str_remove_all('[:digit:]*') %>% 
    str_remove_all('[:punct:]*') %>% 
    str_replace_all('[♥]+', ' ')
  Encoding(x) <- 'ASCII'
  x <- iconv(x, 'ASCII', 'ASCII', sub = '')
  return(x)
}

dat <- dat %>% 
  filter(!is.na(comment)) %>% 
  mutate(date = ifelse(
    grepl('^[A-Z][a-z]+\\s[0-9]+\\,', date),
    date, 
    paste0(date, ', 2018'))) %>% 
  mutate(date = mdy(date),
         title = factor(title)) %>% 
  arrange(desc(date)) %>% 
  distinct() %>% 
  mutate(id = row_number(),
         comment_clean = clean(comment))

my_stop_words <- data_frame(word = c('game','games','play','dota','rocket','league','civ','civil','city', 'dont',
                                     stop_words$word))
```

# Home

## Information {.sidebar}

### Outline {data-icon='fa-game'}
　
This is a mini project about text-mining. 
The dataset is scraped from [Steam Community](https://www.steamcommunity.com). 
There are 6 games considered in this mini project:

**Dota 2**, **Player Unknown's Battle Ground**, **Grand Theft Auto V**, **Civilization VI**, **Cities Skylines**, **Rocket League**.

## HomeInfo


# Basic Info {data-icon='fa-info' data-navmenu="Description"}

```{r}
wordcloud <- dat %>% 
  select(gameId, comment_clean) %>% 
  unnest_tokens(word, comment_clean) %>% 
  anti_join(my_stop_words, by = 'word') %>% 
  count(word, gameId, sort = T) %>% 
  ungroup() %>% 
  group_by(word, gameId) %>% 
  summarise(freq = sum(n)) %>% 
  arrange(gameId,desc(freq))
```

## DataTable {.tabset .tabset-fade}

### DOTA 2

```{r}
dota <- wordcloud %>% filter(gameId == 'dota') %>% select(word, freq)
DT::datatable(dota, options = list(pageLength=7))
```

### Civilization VI

```{r}
civil <- wordcloud %>% filter(gameId == 'Civilization') %>% select(word, freq)
DT::datatable(civil, options = list(pageLength=7))
```

### GTA V

```{r}
gta <- wordcloud %>% filter(gameId == 'GTA5') %>% select(word, freq)
DT::datatable(gta, options = list(pageLength=7))
```

### PUBG

```{r}
pubg <- wordcloud %>% filter(gameId == 'pubg') %>% select(word, freq)
DT::datatable(pubg, options = list(pageLength=7))
```

### Rocket League

```{r}
rl <- wordcloud %>% filter(gameId == 'Rocket_League') %>% select(word, freq)
DT::datatable(rl, options = list(pageLength=7))
```

### Cities Skylines

```{r}
cs <- wordcloud %>% filter(gameId == 'Cities_skylines') %>% select(word, freq)
DT::datatable(cs, options = list(pageLength=7))
```



## {.tabset .tabset-fade}

### DOTA 2

```{r}
dota %>% 
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```

### Civilization VI

```{r}
civil %>%
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```

### GTA V

```{r}
gta %>% 
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```

### PUBG

```{r}
pubg %>% 
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```

### Rocket League

```{r}
rl %>% 
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```

### Cities Skylines

```{r}
cs %>%
  with(wordcloud(word, freq, rot.per = 0.25, max.words = 200, colors=brewer.pal(12, 'Paired'), random.order = FALSE))
```


## Appendix {.sidebar}

This page provides basic word counts for the reviews of each game, along with word-cloud visualizations.

# Comparison {data-icon='fa-balance-scale' data-navmenu="Description"}

## DataTable {.tabset .tabset-fade}

### Word Freq by Opinion

### Word Freq by Game


-----------

## WordCloud {.tabset .tabset-fade}

### Word Comparison Cloud by Opinion

### Word Comparison Cloud by Game


# TF-IDF {data-icon='fa-calculator' data-navmenu='Analysis'}




